Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-03 paper.tex
upadte power section

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.32]{power.png}
  \caption{Electric power generated over time, with in blue the full production,
      in orange the \glspl{LWR} contribution, in green the hight breeding ratio
    \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}
    \label{fig:power}
\end{figure}

@@

\subsection{Uncertainty Measurements}
In this specific study, one will only focus on the uncertainty on the produced
electric power as a function of time, on the total quantity of natural uranium
used and on the total unused fissile inventory (unused reprocessed plutonium).
In order to estimate the total uncertainty on those 3 parameters as well as the
individual contribution of the operational parameters several set of (199) simulations
have been completed.

@@

>>>>

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.32]{power.png}
    \caption{Electric power generated over time, with in blue the full production,
        in orange the \glspl{LWR} contribution, in green the hight breeding ratio
        \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}\label{fig:power}
\end{figure}

@@

\subsection{Uncertainty Measurements}
In this specific study, one will only focus on the uncertainty on the produced
electric power as a function of time, on the total quantity of natural uranium
used and on the total unused fissile inventory (unused reprocessed plutonium).
In order to estimate the total uncertainty on those 3 parameters as well as the
individual contribution of the operational parameters several set of (199)
simulations have been completed.  All uncertainty are computed as the standard
deviation over over all the calculations in the set.

@@

\subsection{Generated Power}
By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
generated power is expected.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.35]{power_full}
    \caption{Electric power generated as a function of time. The black line
        represents the reference calculation and the blue zone
        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:power_full}
\end{figure}

Indeed the transition scenario has been design to allow
all the reactors to receive the fuel as needed allowing them to be producing
power all the time. This ensure that the uncertainty measured on other
parameters are not influence by the reactors miss-loadings.

%%  \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
%%    \centering
%%    \includegraphics[scale=0.37]{power_uncer}
%%    \caption{}\label{fig:power_uncer}
%%  \end{figure}

\subsection{Natural Uranium Consumption}

Figure \ref{fig:unat_full}| represents the cumulative natural uranium
consumption as a function of time.
